---
title: "Investment Report for Projects in `r params$country`"
author: "Data Camp"
output: 
  html_document:
    css: estil.css
    toc: true
    toc_float:
      collapse: false
      smooth_scroll: false
    code_download: true
date: "`r format(Sys.time(), '%d %B %Y')`"
params:
  country: Brazil
  fy: 2018
  year_start: 2017-07-01
  year_end: 2018-06-30
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'center', echo = TRUE)
```

```{r data, include = FALSE}
library(readr)
library(dplyr)
library(ggplot2)

investment_annual_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/d0251f26117bbcf0ea96ac276555b9003f4f7372/investment_annual_summary.csv")
investment_services_projects <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/bcb2e39ecbe521f4b414a21e35f7b8b5c50aec64/investment_services_projects.csv")
```


## Datasets 

### Investment Annual Summary

The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each region for each fiscal year, from 2012 to `r params$fy`.
```{r investment-annual-summary}
ggplot(investment_annual_summary, aes(x = fiscal_year, y = dollars_in_millions, color = region)) +
  geom_line() +
  labs(
    title = "Investment Annual Summary",
    x = "Fiscal Year",
    y = "Dollars in Millions"
  )
```

### Investment Projects in `r params$country`

The `investment_services_projects` dataset provides information about each investment project from 2012 to `r params$fy`. Information listed includes the project name, company name, sector, project status, and investment amounts. Projects that do not have an associated investment amount are excluded from the plot.

```{r country-investment-projects}
country_investment_projects <- investment_services_projects %>%
  filter(country == params$country) 

ggplot(country_investment_projects, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  )
```

### Investment Projects in `r params$country` in `r params$fy`

The `investment_services_projects` dataset was filtered below to focus on information about each investment project from the `r params$fy` fiscal year, and is referred to as `country_annual_investment_projects`. Projects that do not have an associated investment amount are excluded from the plot.
```{r country-annual-investment-projects}
country_annual_investment_projects <- investment_services_projects %>%
  filter(country == params$country,
         date_disclosed >= params$year_start,
         date_disclosed <= params$year_end) 

ggplot(country_annual_investment_projects, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  ) 
```